Instructions for \confname{} Proceedings

### 2019-05-11 papers/EMNLP2019/analysis.tex
attempt at an abstract (too long), updates in agreement table

\begin{table*}
\small
\begin{tabular}{llll|llll|llll}
\toprule
    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
                         domain & \% top &    SN &   =VG &         id &     \% top &    SN &   =VG &             id &     \% top &    SN &   =VG \\
\midrule
         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
 animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
\bottomrule
 all &  0.70 &  1.34 &  0.73            \\

\bottomrule
\end{tabular}
\caption{Agreement in object names for objects of different domains, if applicable, synsets with maximal and minimal agreement (top \%) are shown }
\label{tab:agree}
\end{table*}

>>>>

\begin{table*}
\small
\centering
\begin{tabular}{llll|lll}
\toprule
& \multicolumn{3}{c}{non-canonicalized} & \multicolumn{3}{c}{annotated vs. non-canonicalized} \\
         domain &  \% top &    SD &     N$_{types}$ & Max=VG & \% VG (Micro) & \% VG (Macro) \\
\midrule
         people &  51.88 &  2.13 &  8.60 &  49.77 &        32.25 &        32.25 \\
       clothing &  63.93 &  1.58 &  6.44 &  70.16 &        52.58 &        52.63 \\
           home &  66.35 &  1.50 &  6.31 &  78.48 &        58.82 &        58.92 \\
      buildings &  66.87 &  1.55 &  6.89 &  72.60 &        55.46 &        55.59 \\
           food &  71.27 &  1.30 &  5.49 &  62.89 &        52.11 &        52.25 \\
       vehicles &  71.97 &  1.13 &  4.66 &  71.11 &        60.18 &        60.20 \\
 animals\_plants &  91.26 &  0.44 &  2.68 &  93.84 &        88.01 &        88.01 \\
 \midrule
             all &  69.69 &  1.34 &  5.70 &  72.77 &        58.65 &        58.43 \\
\bottomrule
\end{tabular}
\caption{Agreement in non-canonicalized naming data, and between annotated (original VisualGenome) and non-canonicalized names for different object domains }
\label{tab:agree}
\end{table*}

\begin{table*}
\small
%\begin{tabular}{llll|llll|llll}
%\toprule
%    & \multicolumn{3}{c|}{all synsets} & \multicolumn{4}{c|}{max synset} & \multicolumn{4}{c}{min synset} \\
%                         domain & \% top &    SN &   =VG &         id &     \% top &    SN &   =VG &             id &     \% top &    SN &   =VG \\
%\midrule
%         people &  0.52 &  2.13 &  0.50 &  professional.n.01 &  0.61 &  2.02 &  0.20 &           athlete.n.01 &  0.36 &  2.62 &  0.37 \\
%       clothing &  0.64 &  1.58 &  0.70 &      neckwear.n.01 &  0.79 &  0.91 &  0.77 &          footwear.n.01 &  0.47 &  2.55 &  0.40 \\
%           home &  0.66 &  1.50 &  0.78 &          tool.n.01 &  0.86 &  0.73 &  0.94 &          crockery.n.01 &  0.52 &  1.92 &  0.40 \\
%      buildings &  0.67 &  1.55 &  0.73 &        bridge.n.01 &  0.75 &  1.21 &  0.87 &  place\_of\_worship.n.01 &  0.46 &  2.26 &  0.08 \\
%           food &  0.71 &  1.30 &  0.63 &  edible\_fruit.n.01 &  0.80 &  0.89 &  0.79 &         vegetable.n.01 &  0.53 &  1.97 &  0.15 \\
%       vehicles &  0.72 &  1.13 &  0.71 &         train.n.01 &  0.93 &  0.42 &  0.99 &          aircraft.n.01 &  0.52 &  1.50 &  0.41 \\
% animals,plants &  0.91 &  0.44 &  0.94 &        feline.n.01 &  0.95 &  0.29 &  0.99 &              fish.n.01 &  0.39 &  2.53 &  0.55 \\
%\bottomrule
% all &  0.70 &  1.34 &  0.73            \\
%
%\bottomrule
%\end{tabular}
\begin{tabular}{lllllllllllllll}
\toprule
         domain &  \% top &    SD & Max=VG &   \% VG &         max synset &      \% &    SD & Max=VG &   \% VG &             min synset &      \% &    SD & Max=VG &   \% VG \\
\midrule
         people &  51.88 &  2.13 &  49.77 &  32.25 &  professional.n.01 &  60.67 &  2.02 &  20.00 &  11.67 &           athlete.n.01 &  35.59 &  2.62 &  36.87 &  24.76 \\
       clothing &  63.93 &  1.58 &  70.16 &  52.58 &      neckwear.n.01 &  79.32 &  0.91 &  76.92 &  65.45 &          footwear.n.01 &  46.90 &  2.55 &  40.00 &  25.97 \\
           home &  66.35 &  1.50 &  78.48 &  58.82 &          tool.n.01 &  86.44 &  0.73 &  94.44 &  82.34 &          crockery.n.01 &  51.69 &  1.92 &  40.22 &  29.37 \\
      buildings &  66.87 &  1.55 &  72.60 &  55.46 &        bridge.n.01 &  75.48 &  1.21 &  86.87 &  69.58 &  place\_of\_worship.n.01 &  46.23 &  2.26 &   8.33 &   7.43 \\
            all &  69.69 &  1.34 &  72.77 &  58.65 &               None &   None &  None &   None &   None &                   None &   None &  None &   None &   None \\
           food &  71.27 &  1.30 &  62.89 &  52.11 &  edible\_fruit.n.01 &  79.67 &  0.89 &  78.57 &  69.78 &         vegetable.n.01 &  52.83 &  1.97 &  14.58 &  10.90 \\
       vehicles &  71.97 &  1.13 &  71.11 &  60.18 &         train.n.01 &  92.74 &  0.42 &  99.16 &  92.14 &          aircraft.n.01 &  52.46 &  1.50 &  40.56 &  37.49 \\
 animals\_plants &  91.26 &  0.44 &  93.84 &  88.01 &        feline.n.01 &  94.78 &  0.29 &  98.95 &  94.15 &              fish.n.01 &  38.97 &  2.53 &  54.55 &  32.50 \\
\bottomrule
\end{tabular}
\caption{Agreement in object names for objects of different domains, if applicable, synsets with maximal and minimal agreement (top \%) are shown }
\label{tab:agree}
\end{table*}
